---
title: "R Notebook for naturalness/acceptability judgments linguistic experiments"
output: html_notebook
author: "Masha Onoeva"
date: "2024-05-07"
---

Hi! This is an R notebook created by Masha Onoeva (me). It describes the steps that are required for the analysis of naturalness/acceptability judgments linguistic experiments. I use the experiment that I did with Radek Šimík testing Russian negated polar questions in different contexts as the example data. The experiment was run on LRex, so your raw data can be different if you use a different platform.
```{r}
library(tidyverse) # THE package for us, it contains ggplot2, tidyr, dplyr, readr and more

```
## 1. Loading data
Setting the working directory and loading data. There is an option to download the version without abandoned trials and I load it here. Then I remove the unnecessary example items.
```{r}
# setting the dir
setwd("/Users/maria.onoeva/Desktop/new_folder/GitHub/stat-repo/R_script_new")

# loading all data
all_df <-
  read_delim("queslav_neg_mo_RESULTS_2023-03-06-0953_noaband.csv", ";",
                                             escape_double = FALSE,
                                             trim_ws = TRUE,
                                             show_col_types = FALSE)

# removing example items
main_df <- all_df[-which(all_df$materials=="1_examples"),]
main_df %>%
    summarise(participant = n(), .by = NULL, .groups = NULL)
```
## 2. Fillers and unreliable participants

```{r}



```
